\documentclass[10pt]{article}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[resetlabels]{multibib}
\usepackage[ManyBibs,NoDate]{currvita}
% Initialize each paper type for which you need a bibliography.
% Just a dummy parameter is necessary.

% Better for lists with 1-2 items and short descriptions
\newenvironment{sublist}{%
	\begin{list}{}{%
		\setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
		\setlength{\topsep}{0em}\setlength{\parskip}{0em}%
	}%
}%
{ \end{list} }

% Better for lists with more than 2 items and/or long descriptions
\newenvironment{subbulletlist}{%
	\begin{list}{\labelitemii}{%
		\setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
	}%
}%
{ \end{list} }

\begin{document}

% We'll use this length to change the defaults in some of our lists.
\newlength{\oldcvlabelwidth}
\renewcommand*{\cvbibname}{}

% This is what will appear at the very top of your CV.
\begin{cv}{Kimball Johnson\\{\large \itshape Curriculum Vitae}}

% Items have more vertical space between them than line breaks.
% Note: if you want a linebreak after each cvlist title, you can do:
% \begin{cvlist}{Title \hspace{3in}}
\begin{cvlist}{Contact}
	\item
	14 Great Avenham Street\\
	Preston\\
	Lancashire\\
	PR1 3TD
	\item Phone: 01772 592295\\
	Mobile: 07970252372
	\item kimball@bowerham.net
\end{cvlist}

\begin{cvlist}{Education}
	\item \emph{BSc II(ii)(honours) Computer Science}, 2002- 2005\\
	Lancaster University
    \item \emph{Electronic and Computer Engineering First Year} 2000-2001\\
    University of York (Withdrawn)
\end{cvlist}

% cvlist items can take dates as a parameter.
\begin{cvlist}{Employment}

    \item[05/2013 - date] Senior Systems Engineer\\
    One Connect Limited\\
    Preston, Lancashire
    \item[05/2011 - 04/2013] Systems Developer\\
    One Connect Limited\\
    Preston, Lancashire
    \item[02/2011 - 05/2011] Systems Developer\\
    Lancashire County Council\\
    Preston, Lancashire
	\item[07/2007 - 02/2011] Systems Developer\\
	Lancaster University Network Systems Ltd (LUNS)\\
	Lancaster, Lancashire
    \item[09/2005 - 07/2007] Software Developer \\
    Auto Execution, Research and Development, Bloomberg LP,
    London
    \item[07/2005 - 09/2005] Systems Developer \\ 
	Lancaster University Network Systems Ltd (LUNS)\\
	Lancaster, Lancashire
    \item[09/2005 - 07/2007] Software Developer Internship\\
    Trading Systems, Research and Development, Bloomberg LP,
    London
    \item[05/2004 - 06/2004, 09/2004-06/2005] Support Assistant\\
    Lancaster University
    \item[04/2002 - 09/2002] Audio Visual Technician\\
    University of York
\end{cvlist}
\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Technical Skills}
		\item C++, C, Java (J2SE), Perl, Ruby, Rails, Objective C, Fortran, PHP
		\item Chef
		\item Postgresql, MySQL
		\item UML, Agile, Test Driven Development, SCRUM, JUnit
		\item TCP/IP, Linux, Windows
		\item ITIL v3 Foundation Certified, PRINCE2 Foundation Certified
\end{cvlist}
\setlength{\cvlabelwidth}{\oldcvlabelwidth}
\pagebreak

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\cvlabelwidth}{1em}
\renewcommand*{\bibindent}{1.5em}

\begin{cvlist}{Experience}
    \item \textbf{Lancashire County Council/One Connect Limited}

    On the 14th of February 2011 the contract between CLEO and LUNS (below)
    ended, and LCC brought the work in-house.  As a result I was transferred into
    the council through TUPE and continued with the same duties, with 
	a greater responsibility of support due to a smaller team.  In May 2011 the council 
	formally entered into a Strategic Partnership with BT, forming One Connect Limited, 
	and many of the staff were seconded into the organisation.
	
	Upon the transfer much of core infrastructure was not part of the transfered contract 
	so I have had to rebuild it.
	This includes service monitoring, centralised configuration systems and 
	package management and deployment systems.  With the benefit of a green field
	environment, I have designed a new system based on the Chef Configuration management
	system, modified to allow for simple disaster recovery, maintaining copies of all
	configuration in the central server, and thus on backup tapes. LCC, as with LUNS,
	follow the ITIL v3 Service Methodology.   
	
	Key Skills: ITIL, PRINCE, Perl, PHP, Ruby, Chef, JavaScript, JQuery, 
	SQL, ADODB, SQLite, Apache HTTP, H323, Linux, Windows, Active Directory, LDAP, 
	Kerberos, GIT, Subversion, Shell Scripting
	
	\item \textbf{LUNS}

    LUNS's primary business was a contract with the Cumbria and Lancashire
    Education Online (CLEO) Regional Broadband Consortium.  This contract was
    to provide all of the network systems, and a large proportion of the
    central computer systems for the schools in the two counties.
    Additionally they had a separate one contract with Cumbria County Council to
    provide further central software services for Cumbrian schools. All projects 
	were managed using PRINCE2 and service was managed under the ITIL v3 Best Practices.
	\begin{subbulletlist}
    \item Network Edge Device

        One of my main projects at LUNS is the ongoing development of the
        Network Edge Device that is installed into every school in the two
        counties.  This device, based on Debian GNU/Linux, is for local 
        web caching, filtering and content provision.  It is designed to 
        be centrally managed, and such that it can recover from almost any
        corruption or configuration problems simply with a reboot. I have 
        been involved with all aspects of this project, particularly with the 
        database system, and stored procedures. Another major aspect of this 
        project has been integration of the web proxy authentication with
        Microsoft Active Directory, initially through NTLM, and most recently
        Kerberos. 
    \item Dashboard Management system

		As part of the NED project described above, there was need for a central 
		web based management system.  To this end we designed a modular PHP5 class 
		based framework, and a hierarchal data structure. I was greatly involved 
		in this system, and wholly responsible for the database development. This was 
		developed in PostgreSQL with PL/Perl stored procedures.
    \item Cumbrian Shared Hosting 

        Another major project has been the re-development of the Cumbrian
        schools shared hosting solution.  I was the project lead for this,
        organising the work for myself and my colleagues to produce a new 
        secure hosting solution for the schools.  I designed a 
        solution that takes advantage of separation of concerns with Linux 
        Virtual Servers, and by employing various security features to help
        prevent spread of any attacks or exploits from one site to another.
    \item Video Conferencing 

        CLEO provide a video conferencing service to schools and museums in
        both counties, based on the GnuGK gatekeeper software.  I have
        been the lead on this service since I started at LUNS full time, and
        have been responsible for a migration of the management and
        authentication system from the old, hard to manage system, to integrate
        with the dashboard configuration system, used by the NED project.
	\end{subbulletlist}
	
	Key Skills: ITIL, PRINCE, Perl, PHP, JavaScript, JQuery,  SQL, ADODB, SQLite,
	Apache HTTP, H323, Linux, Windows, Active Directory, LDAP, Kerberos, GIT, 
	Subversion, Shell Scripting
	\item \textbf{Bloomberg}

	\begin{subbulletlist}
    \item E-Bond Trading Platform

    After the 10 week training class for the full time position, I became part of 
    the Auto Execution applications development team, initially working on the 
    E-Bond electronic trading platform. I quickly took over as the main support 
    contact for the back end server programs running the application, and 
    additionally developed many new features as the project phases continued.
    This was developed in C and C++, and GTK for the User Interface.  This low latency 
	real-time system was in use at the time as the canonical trading platform for 
	many emerging bond markets.
    
    \item T-Zero Integration

    The next major project I worked on was integration with the T-Zero
    Credit Default Swap trade reporting system. For this greenfield project 
	I designed the back-end multi-threaded server application from scratch to integrate 
	with their Java Enterprise application server.  As this systems was developed
	in Java it provided a great challenge integrating new technologies with the dated 
    existing Bloomberg Systems.  
	\end{subbulletlist}

	Key Skills: Java, C, C++, GTK, Fortran, SQL, UML, JUnit, Shell Scripting, UML 
	\item \textbf{LUNS (Summer Placement)}

    During my summer placement with LUNS, I was employed to support
    the CLEO network systems. This entailed writing support systems for 
    their video conferencing web based billing system using PHP and Perl. 
    I was also involved in the start of the Local Loop Unbundling Project; 
    this involved meeting with British Telecom, and
    understanding their proprietary XML based messaging protocol.

	Key Skills: PHP, Perl, XML
    \item \textbf{Bloomberg Internship}

    During the summer vacation 2004, I was selected for an internship with the 
    Research and Development department at Bloomberg LP in London. During this 
    period I was part of the Trading Systems team, and completed several projects
    to improve the quality of the Bloomberg Professional system.

	Key Skills: C, C++, Fortran, XML, XSLT, PHP, HDODB
    \item \textbf{Lancaster University}

    Whilst a student at Lancaster University I worked as a Support Technician for
    the student residential network. This involved configuration of students' 
    computers for use on the network, and removal of viruses and other system
    problems, that caused system and network problems for all the users on the network.  
    This was primarily a technical support role working with Windows Operation 
    systems, but I also provided support for Linux and MacOSX systems.

	Key Skills: Windows(9x, XP), Linux, MacOSX
    \item \textbf{University of York}

    For the University of York I worked in the Audio Visual Department as a 
    technician. This involved setting up computer projectors and PA Equipment for 
    Lectures during term time, and providing technical assistance for delegates 
    during the conferences in the holiday period. I also started to write a 
    web-based diary system, using ColdFusion and Interbase on a Solaris
    system, sadly I started at Lancaster before this was able to be completed

 	Key Skills: Cold Fusion, Interbase, PHP

%    \item \textbf{Norwich Union Insurance PLC}
%    Here I was employed to update the project tracking and management system for 
%    the marketing department. The company had recently merged with CGU Plc and as 
%    such there was a large amount of inconsistency between the two systems. I was 
%    briefed to resolve the errors and to consult with the staff using the system 
%    for their feedback, in order to implement new features.

%    \item \textbf{Vox Technology Ltd}
%    Vox Technology Ltd is a small computer company based in Partridge Green, West 
%    Sussex. They build bespoke computer systems, and have a large customer base in 
%    Sussex and Surrey.
%    I was employed as a member of the technical support team, visiting customer 
%    sites to solve more complex problems. I installed network systems, and 
%    assembled and installed all types of computers, from home machines, to large 
%    business servers. I wrote software for internal use, using Microsoft Access 
%    and Visual Basic, and also updated customers database systems for Y2K 
%    compliance.

\end{cvlist}

\pagebreak
\begin{cvlist}{Extracurricular}
\item Student Radio

Whilst I was studying at York University I became an active member of the 
University Radio, where I held the post of Assistant Computing Officer. 
I assisted the computing officer in the running of the computer equipment
in the radio station, including the database systems, and the security of the 
main server. I was previously the web-master, responsible for the maintenance of
the website. I also was heavily involved with the organisation and preparation 
of several outside broadcasts, including the Student Union Elections. I 
presented a number of shows for the radio, including co-hosting the Breakfast 
Show.  I was also involved with the Campus radio station at Lancaster, where I 
was the Systems Administrator, and maintained a network of a Linux 
server, Linux workstation, and 6 Windows workstations.
\item RAG

I was on the York RAG Committee, as the Media Promotions Officer. This
involved filming the various RAG fund raising events. I also made a 
promotional video, designed to encourage students to get involved in RAG and 
hitchhiked to Paris two years running in aid of Children in Need.
\item Misc

I enjoy water sports, including dinghy sailing, kayaking, windsurfing and 
Canadian canoeing. I am a PADI Advanced Open Water diver and have dived in 
various locations around the world.
I relax by reading, particularly Science Fiction and Fantasy and 
Action Thrillers, and experimenting with programming, and video/sound editing 
on my computer.
On a more cultural side, I am a keen singer, and have been involved in both
the University Choir, and Lancaster Male Voice Choir.  I also enjoy going to
concerts both classical and contemporary, and Musical Theatre.
\end{cvlist}
\end{cv}
\end{document}

